---
title: "Preliminary Report April 3"
author: "Joey"
date: "`r Sys.Date()`"
output: html_document
---

```{r, set-chunk-options, echo=FALSE}

library(knitr)
opts_chunk$set(echo = FALSE, 
               warning = FALSE, 
               message = FALSE)
```
# Introduction
```{r, loading-in-data}

data_1<- readRDS(file = here::here("output/variablized_cleaned_data.rds"))

```
## Data Description
The de-identified dataset was collected by the Atlanta Center for Microsystems Engineered Point of Care Technologies (ACME-POCT) as part of test verification activities for the Rapid Acceleration of Diagnostics (RADx) initiative to develop and evaluate novel viral diagnostics for COVID-19. Surveys and anterior nasal swabs were collected from `r nrow(data)` participants and included in the current analysis. 

## Analysis Objectives
The preliminary analysis will identify and count the number of PCR positives for each virus tested (COVID-19, Influenza A, Influenza B, and RSV). We will also create a variable for symptom duration, defined as the difference between symptom onset and the visit date. We used the visit date and patient reported recent vaccination date for the COVID vaccine, the Omicron Booster, and the Flu vaccine to stratify by time since vaccination. First we will plot the PCR Ct values, which is a surrogate for viral load, from the positive individuals by days of symptom duration. Future analyses will include the time since vaccination variables.



# Descriptive Analyses of RADX Data

## Table 1
Characteristics of `r nrow(data_1)` participants are displayed in the table below.
```{r, table-one}
table_one <- readRDS(
  file = here::here("output/table1.rds"))

table_one

```
## COVID-19

```{r, figure-1}
#| echo= FALSE,
#| message = FALSE,
#| fig.align = "center",
#| out.width = "400px"
library(dplyr)
covid_ct_symptom_group_filtered <- data_1 %>%
  filter(covid_result_factor != "Negative" & !is.na(ct_value_1))

knitr::include_graphics(
  here::here("output/covid_boxplot.png")
)

```
There were `r sum(data_1$covid_result_factor == "Positive", na.rm = TRUE)` PCR Positives for Sars-CoV-2. Of these, `r nrow(covid_ct_symptom_group_filtered)` had Ct values reported in their chart. Above is a figure of Ct Values by days of symptom duration.

## Flu A


```{r, figure-2}
#| echo= FALSE,
#| message = FALSE,
#| fig.align = "center",
#| out.width = "400px"

fluA_ct_symptom_group_filtered <- data_1 %>%
  filter(fluA_result_factor != "Negative" & !is.na(flua_ct1))

knitr::include_graphics(
  here::here("output/fluA_boxplot.png")
)

```

There were `r sum(data_1$fluA_result_factor == "Positive", na.rm = TRUE)` PCR Positives for Influenza A. Of these, `r nrow(fluA_ct_symptom_group_filtered)` had Ct values reported in their chart. Above is a figure of Ct Values by days of symptom duration.

## Flu B


```{r, figure-3}
#| echo= FALSE,
#| message = FALSE,
#| fig.align = "center",
#| out.width = "400px"

fluB_ct_symptom_group_filtered <- data_1 %>%
  filter(fluB_result_factor != "Negative" & !is.na(flub_ct1))

knitr::include_graphics(
  here::here("output/fluB_boxplot.png")
)
```
There were `r sum(data_1$fluB_result_factor == "Positive", na.rm = TRUE)` PCR Positives for Influenza B. Of these, `r nrow(fluB_ct_symptom_group_filtered)` had Ct values reported in their chart. Above is a figure of Ct Values by days of symptom duration.

## RSV

```{r, figure-4}
#| echo= FALSE,
#| message = FALSE,
#| fig.align = "center",
#| out.width = "400px"

rsv_ct_symptom_group_filtered <- data_1 %>%
  filter(rsv_result_factor != "Negative" & !is.na(rsv_ct))

knitr::include_graphics(
  here::here("output/rsv_boxplot.png")
)

```
There were `r sum(data_1$rsv_result_factor == "Positive", na.rm = TRUE)` PCR Positives for RSV. Of these, `r nrow(rsv_ct_symptom_group_filtered)` had Ct values reported in their chart. Above is a figure of Ct Values by days of symptom duration.
